\documentclass{article}
% Starting with the following template:
% 
% Resume template for Brown's joint CareerLAB and Science Center
% LaTeX/Resume workshop
% (http://bit.ly/resumeTemplate)

% Allow picking fonts
\usepackage{fontspec}
\usepackage[slantfont, boldfont]{xeCJK}

% Chinese
\setCJKmainfont{HanaMinA}
\setCJKsansfont{HanaMinA}
\setCJKmonofont{HanaMinA}
\XeTeXlinebreaklocale "zh"
\XeTeXlinebreakskip = 0pt plus 1pt

% English
\setmainfont[Ligatures=TeX]{Latin Modern Roman}
\setsansfont[Ligatures=TeX]{TeX Gyre Heros}
\setmonofont[Ligatures=TeX]{Berkeley Mono}

% Shrink margins
\usepackage[margin=0.7in]{geometry}

% Itemize spacing
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0.4em}

% For hyperlinks
\usepackage{hyperref}

% For making compact lists with itemize* environment
\usepackage{mdwlist}

% Fancy sections
\newcommand{\ressection}[1]{\noindent{\large\textbf{#1}}\vspace{2pt}\hrule\vspace{4pt}}

% For items with dates: \hfill fills up horizontal space until the
% words to the left and the right are as far apart as possible
\newcommand{\leftandright}[2]{\noindent\textbf{#1}\hfill\textbf{#2}}

% Remove page numbering
\pagestyle{empty}

\begin{document}

%% Change font family
\sffamily

\noindent
\begin{center}
    
\textbf{\huge{Daniel~Klein 微担意}}

web: \href{http://mesokurtosis.com}{\texttt{mesokurtosis.com}}
\textbullet\,
github: \href{https://github.com/othercriteria}{\texttt{othercriteria}}
\textbullet\,
email: \href{mailto:daniel.l.klein@proton.me}{\texttt{daniel.l.klein@proton.me}}
\textbullet\,
\texttt{952.454.4197}

\end{center}

\ressection{Experience}

\leftandright{Oracle Corporation (Advertising and Customer Experience, Moat)}{2019 -- present} \\
\textit{Principal Data Scientist}

\begin{itemize*}
\item Develop and maintain streaming pipelines for Invalid Traffic
  detection, consuming $\sim$100,000 events / sec.
\item Ensure use of appropriate data- and statistics-driven methods
  within-team, cross-team, and externally.
\end{itemize*}

\leftandright{DMG Blockchain Solutions (Blockseer)}{2018 -- 2019} \\
\textit{Senior Software Engineer}

\begin{itemize*}
\item Led rewrite of Bitcoin address clustering (EMR, Scala, GraphX);
  1.2 TB blockchain processed in $\sim$6 hours.
\item Validated novel Bitcoin transaction classification method using
  custom DeepWalk implementation.
\end{itemize*}

\leftandright{RealScout}{2016 -- 2017} \\
\textit{Data Scientist}

\begin{itemize*}
\item Productionized insights from agent-agent modeling into
  user-facing Recommended Listing feature.
\item Automated schema mapping for ETL of external listing databases
  (MLS) using gradient boosting match model.
\item Built out Bayesian models for sales price and days-on-market
  prediction with near-Zillow/Redfin accuracy.
\end{itemize*}

\leftandright{Radius Intelligence, RealScout, Neighborly (rotations)}{2016} \\
\textit{Data Science apprentice (Catenus, 8VC)} \\

\leftandright{TransForm Pharmaceuticals, Inc.}{2006 -- 2008} \\
\textit{Assistant Scientist, Scientific Computation}

\begin{itemize*}
\item Delivered tooling to support computational chemistry research
  and data integration (HPLC, IR, UV-Vis) for lab automation
  platforms.
\end{itemize*}

\leftandright{Williams College, Dept.\ of Biology}{2005} \\
\textit{Research Assistant}

\begin{itemize*}
\item Planned and implemented experimental design and data analysis
  for field research project.
\end{itemize*}

\leftandright{University of Minnesota, Dept.\ of Ecology and
  Evolutionary Biology}{2003, 2004} \\
\textit{Research Intern}

\begin{itemize*}
\item Developed and analyzed numerical results from novel model for ecological
  community assembly.
\end{itemize*}

\ressection{Education}

\leftandright{Brown University, \textmd{Ph.D. Applied
    Mathematics}}{2008 -- 2016 (defended)}
\begin{itemize*}
\item Advised by \href{http://www.dam.brown.edu/people/harrison}{Matt
  Harrison}; research on statistical inference in settings of extreme
  data sparsity or imbalance.
\item TA for Intro Stats, Math Stats I/II, Recent Applications in
  Probability and Statistics.
\end{itemize*}

\leftandright{Williams College, \textmd{B.A.\ Mathematics and
    Biology}}{2006}
\begin{itemize*}
\item Departmental honors in Biology, with thesis ``Understanding
  aggregation in the membracid \emph{Publilia concava}: using models
  to disentangle processes''.
\end{itemize*}

\ressection{Relevant coursework}

\begin{itemize*}
\item Foundational CS: Data Structures, Algorithm Design/Analysis, PL,
  PL Theory.
\item Bayesian Stats, Biostats, graduate Math Stats I/II, graduate
  Probability/Stochastics.
\item Seminars in Graphical Models, Bayesian Nonparametrics, Network
  Models.
\item Computational Biology: dynamic programming, approximation
  algorithms, HMMs, etc.
\end{itemize*}

\ressection{Value over replacement player / comparative advantage}

\noindent Beyond standard

\begin{itemize*}

\item Enthusiastic: Python(+mypy), R, C/C++, SQL. Grudging:
  JavaScript, Matlab, Scala. Exploring: Rust, Haskell.
\item Statistics, numerics, and visualization libraries:
  numpy/scipy/pandas/scikit-learn, TensorFlow, Stan, PyMC3, D3, etc.
\item Familiarity with software engineering tooling (git, build
  systems, CI, etc.), web development (client-server, HTML, CSS,
  Hakyll, etc.), and cloud deployment (Docker, AWS, etc.), distributed
  computing (Hadoop, Spark, etc.).
\item Product mindset (quantifying and measuring value creation,
  growth modeling, UX design, product management).
\end{itemize*}

\end{document}
